---
title: "Yu_Guo_hw5"
author: "Yu_Aruna"
date: "2/26/2021"
output: word_document
---

```{r}

         Stockreturns <- c(-8.36,   1.63,  -2.27, -2.93,  -2.70, 
                           -2.93, -9.14, -2.64, 6.82,   -2.35, 
                           -3.58,   6.13,   7.00, -15.25, -8.66,
                           -1.03, -9.16,  -1.25, -1.22,  -10.27,
                           -5.11, -0.80,  -1.44,  1.28,  -0.65,
                            4.34,   12.22, -7.21, -0.09, 7.34, 
                            5.04,  -7.24,  -2.14, -1.01,  -1.41, 
                            12.03, -2.53,  4.33,  1.35)

```

#1) Use and show R code to find the mean of the sample data.

```{r}
mean = mean(Stockreturns)
```


#2) Use and show R code to find the standard deviation of the sample data

```{r}
sd = sd(Stockreturns)
```


#3) Assuming a normal distribution, use and show R code to find the proportion of returns that are less than  -1.5.

```{r}
pnorm(q = -1.5, mean = mu, sd = sd)
```


#4) Assuming a normal distribution, use and show R code to find return value that is above 70% of the returns

```{r}
qnorm(p = 0.3, mean = mean, sd = sd)
```


#5) Use and show R code to find Q1 for the data.

```{r}
summary(Stockreturns)
```


#6) Explore the data by producing and examining a boxplot and checking for normality.

```{r}
boxplot(Stockreturns)
qqnorm(Stockreturns)
qqline(Stockreturns)
```


#7) State the appropriate null and alternative hypothesis required for the appropriate t test. The average of the S&P 500 stock index for the same period was 0.95%
# H(0) :  broker perform equal to 0.95
# H(A) :  broker perform worse than 0.95
 


#8) Use and show R code that will output the needed p value and confidence interval to determine if the null hypothesis should be rejected. Since the p value is 0.01827 less than 0.05, we have the evidence that we can reject the H(0).

```{r}
t.test(Stockreturns, mu = .95, alternative = "less", conf.level = .95)
 #t.test(Stockreturns, mu, conf.level = .95)
```


#9) Now answer the question originally stated.  Does the broker perform worse than average? (Explain or justify in two or three sentences) Since the p value is 0.01827 less than 0.05, we have the evidence that we can reject the H(0). So it is possible that the broker perform worse than average.
